### 2016-06-22 paper/numerical_experiments.tex
added 3D setup figures
small edits

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-3}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a domain twice the length in the $x_1$ and $x_2$ directions. The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}. We again require regularization, and use the regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.3\textwidth]{placeholder.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet is small enough to not require stabilization.

@@

>>>>

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions. The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}. We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_arial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet is small enough to not require stabilization.

@@

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows ...
%
\begin{tabular}{c|c|c|c|c|c}
Case & $\%HF$ & QoI & Relative Error (Estimated) & Relative Error (Actual) & Time (s) \\
LF & 0 & 1068856 &  &  &  \\
MF01 & 16.7 &  &  &  &  \\
MF02 & 29.0 &  &  &  &  \\
MF03 & 42.3 &  &  &  &  \\
HF & 100 & 547420 &  &  &  \\
\caption{...}
\end{tabular}
